Enforced Invariant Confluence

### 2018-02-15 doc/paper_redux/diconfluence_direduction.tex
Cleaned up diconfluence_direduction section.

\input{diconfluence_direduction.fig}

We can also interpret \dIconfluence{} and \dIreduction{} using the graph-based
model of \Iconfluence{}, as illustrated in
\figref{diconfluence_and_direduction}. Intuitively, \dIconfluence{} is the
property that any two divergent join-free paths that satisfy $I$ can be joined
together to form a new state that satisfies $I$. \dIreduction{} is the property
that the join of any two divergent join-free paths that satisfy $I$ can be
replaced with a single join-free path that satisfies $I$. Both conditions
involve diamond diagrams, hence the names \dIconfluence{} and \dIreduction{}.

\begin{claim}\clmlabel{diconfluence_direducible_implies_iconfluence}
  If $T$ is \dIconfluent{} and \dIreducible, then it is \Iconfluent.
\end{claim}
\begin{proof}
  First, we prove that for all join-free $e$, if $\Irec{e}$ then there exists a
  join free $e'$ where $\Irec{e'}$ and $eval(e) = eval(e')$. We proceed by a
  pretty straightforward structural induction on $e$.
  \begin{itemize}
    \item \textbf{Case 1: $e = s_0$.}
      Trivially, $e' = s_0.$

@@

    \item \textbf{Case 3: $e = e_1 \join e_2$.}
      $\Irec{e_1 \join e_2}$, so $\Irec{e_1}$ and $\Irec{e_2}$. Thus, by the
      inductive hypothesis, there exist join-free expressions $e_1'$ and $e_2'$
      where $eval(e_1') = eval(e_1)$, $\Irec{e_1'}$, $eval(e_2') = eval(e_2)$,
      and $\Irec{e_2'}$. Let $e'' = e_1' \join e_2'$
      \[
        eval(e'')
          = eval(e_1' \join e_2')
          = eval(e_1') \join eval(e_2')
          = eval(e_1) \join eval(e_2)
          = eval(e_1 \join e_2)
          = eval(e)
      \]
      This implies that $\Irec{e''}$. Because $T$ is \dIreducible, there exists
      a join-free $e'$ such that $\Irec{e'}$ and $eval(e') = eval(e'') =
      eval(e)$.
  \end{itemize}

>>>>

% \input{diconfluence_direduction.fig}
%
% We can also interpret \dIconfluence{} and \dIreduction{} using the graph-based
% model of \Iconfluence{}, as illustrated in
% \figref{diconfluence_and_direduction}. Intuitively, \dIconfluence{} is the
% property that any two divergent join-free paths that satisfy $I$ can be joined
% together to form a new state that satisfies $I$. \dIreduction{} is the property
% that the join of any two divergent join-free paths that satisfy $I$ can be
% replaced with a single join-free path that satisfies $I$. Both conditions
% involve diamond diagrams, hence the names \dIconfluence{} and \dIreduction{}.

\begin{claim}\clmlabel{diconfluence_direducible_implies_iconfluence}
  If $T$ is \dIconfluent{} and \dIreducible, then it is \Iconfluent.
\end{claim}
\begin{proof}
  First, we prove that for all join-free $e$, if $\Irec{e}$ then there exists a
  join-free $e'$ where $\Irec{e'}$ and $eval(e) = eval(e')$. We proceed by a
  pretty straightforward structural induction on $e$.
  \begin{itemize}
    \item \textbf{Case 1: $e = s_0$.}
      Trivially, $e' = s_0.$

@@

    \item \textbf{Case 3: $e = e_1 \join e_2$.}
      $\Irec{e_1 \join e_2}$, so $\Irec{e_1}$ and $\Irec{e_2}$. Thus, by the
      inductive hypothesis, there exist join-free expressions $e_1'$ and $e_2'$
      where $eval(e_1') = eval(e_1)$, $\Irec{e_1'}$, $eval(e_2') = eval(e_2)$,
      and $\Irec{e_2'}$. Let $e'' = e_1' \join e_2'$
      \begin{align*}
        eval(e'')
        &= eval(e_1' \join e_2') \\
        &= eval(e_1') \join eval(e_2') \\
        &= eval(e_1) \join eval(e_2) \\
        &= eval(e_1 \join e_2) \\
        &= eval(e)
      \end{align*}
      This implies that $\Irec{e''}$. Because $T$ is \dIreducible, there exists
      a join-free $e'$ such that $\Irec{e'}$ and $eval(e') = eval(e'') =
      eval(e)$.
  \end{itemize}

### 2018-02-15 doc/paper_redux/iconfluence.tex
Cleaned up diconfluence_direduction section.

\section{\Iconfluence{}}
A \defword{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set
of states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to
S$ is a commutative binary merge operator that we call join. A
\defword{transaction} $t: S \to S$ is a function that maps one state to
another.  An \defword{invariant} $I: S \to \set{\text{true}, \text{false}}$ is
a predicate on states. For example, $(\nats, +)$ is a distributed object, $t(x)
= 2x$ is a transaction, and $I(x) = x \geq 0$ is an invariant.

>>>>

\section{\Iconfluence{}}
A \defword{distributed object} is a triple $(S, s_0, \join)$ where $S$ is a set
of states, $s_0 \in S$ is a designated start state, and $\join: S \times S \to
S$ is a binary merge operator that we call join. A \defword{transaction} $t: S
\to S$ is a function that maps one state to another.  An \defword{invariant}
$I: S \to \set{\text{true}, \text{false}}$ is a predicate on states. For
example, $(\nats, +)$ is a distributed object, $t(x) = 2x$ is a transaction,
and $I(x) = x \geq 0$ is an invariant.
